---
title: "MY Dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    orientation: rows
    vertical_layout: fill
    social: ["twitter","facebook","menu"]
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(dplyr)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(openintro)
library(highcharter)
library(ggvis)

```

```{r}
data<- read.csv("~/R FILES/dashborad/VehicleFailure.csv")
```

```{r}
mycolors<- c("blue","#FFC125","darkgreen","darkorange")
```

interactive data visualization
======================================================

Row
----------------------------------------------------------

### car failure analysis

```{r}
valueBox(paste("Failure"),
         color = "orange")
```

### car failure in us
```{r}
valueBox(length(data$State),
         icon = "fa-user")
```

### **labor cost**
```{r}
gauge(round(mean(data$lc),
            digits = 2),
            min =  0,
            max = 360,
            gaugeSectors(success = c(0,150),
                         warning = c(150,240),
                         danger = c(240,360),
                         colors = c("green","yellow","red")))
```
### massachusetts

```{r}
valueBox(sum(data$State == "MA"),
         icon = "fa-building")
```

### california
```{r}
valueBox(sum(data$State == "CA"),
         icon = "fa-building")
```

### Taxes
```{r}
valueBox(sum(data$State == "TX"),
         icon = "fa-building")
```

### florida
```{r}
valueBox(sum(data$State == "FL"),
         icon = "fa-building")
```

Row
---------------------------------
### failure by state
```{r}
p1 <- data%>%
    group_by(State)%>%
      summarise(count=n()) %>%
        plot_ly(x =~State,
                y=~count,
                color = rainbow(51),
                type = "bar")%>%
  layout(xaxis = list(title = "failure by state"),
         yaxis = list(title = 'Count'))
p1
```

### top state

```{r}
p2<-data%>%
  group_by(State)%>%
    summarise(count=n())%>%
      filter(count>50)%>%
      plot_ly(labels=~State,values=~count,marker=list(colors=mycolors))%>%add_pie(hole = 0.5)%>%
  layout(xaixs = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgird = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgird = F))
p2
  
```

### failure month vs failure mileage

```{r}
p3<- plot_ly(data , 
             x = ~fm,
             y = ~Mileage,
             text = paste("FM" , data$fm,
                          "mileage",data$Mileage),
             type = "bar")%>%
  layout(xaixs = list(title = "failure mileage"),
         yaxis = list(title = "mileage"))
p3
```
Row
---------------------------------------------

### scatter plot of month vs mileage

```{r}
p4<- plot_ly(data , x=~fm)%>%
        add_markers(y = ~Mileage,
                    text= ~paste("mileage" ,Mileage),
                    showlegend = F)%>%
        add_lines(y = ~fitted(loess(Mileage~fm)),
                  name = "loss smoother",
                  color = I("#FFC125"),
                  showlegend = T,
                  line = list(width=5))%>%
  layout(xaxis=list(title = "month"),
         yaxis = list(title = "mileage"))
p4
```

### box plot of top state 
```{r}
data %>%
  group_by(State)%>%
  ggvis(~State , ~lc)%>%
  layer_boxplots()
```

Map
======================================================

### map

```{r}
car <-data%>%
  group_by(State)%>%
  summarise(total = n())
car$State <- abbr2state(car$State)

highchart()%>%
  hc_title(text = "car failure in us")%>%
  hc_subtitle(text = "source : vehiclefailure.csv")%>%
  hc_add_series_map(usgeojson , car , name = "State" ,value = "total" , joinBy = c("woename", "State"))%>% hc_mapNavigation(enabled =T)
```


Table data
=====================================================

```{r}
datatable(data , 
          caption = "failure data",
          rownames = T , 
          filter = "top" , 
          options = list(pagelength = 30))
```

pivot table 
=====================================================
```{r}
rpivotTable(data,
            aggregatorName = "Count",
            cols = "fm",
            rows = "State",
            rendererName = "Heatmap")
```

Summary {data-orientation=columns}
====================================================================
Column
-----------------------------------------
### max failure month
```{r}
valueBox(max(data$fm),
         icon = "fa-user")
```

### average labor cost 
```{r}
valueBox(round(mean(data$lc),
               digits = 2),
         icon = "fa-area-chart")
```


### avrage mileage at failure
```{r}
valueBox(round(mean(data$Mileage),
               digits = 2),
         icon = "fa-area-chart")
```

Column
-----------------------------------------
Report 

* this is a report on`r length(data$fm)`car failure.

* the average labor cost was `r mean(data$lc)`.
* the average material cost was `r mean(data$mc)`
this report was generateted `r format(Sys.Date() , format = "%B %d , %Y")`

About report 
==================================
Created by : omkar sutar 
resource : YouTube

